Supplemental material for `Eliminating prior-bias from sparse-projection tomographic reconstructions'

### 2020-07-22 paper/response.tex

\textbf{Response:} The optimal values of parameters obtained by tuning RMSE were found to be different from those obtained by tuning SSIM. Hence, for consistency, we choose only one metric (SSIM) to report accuracy of all reconstructions.
Moreover, SSIM gives us the flexibility to measure the fidelity of the structural content of our reconstruction with respect to that of test volume.\\

\textcolor{blue}{\textbf{R1-C8:}\textit{ For instance, in Fig. 10 (e), the region within the ROI seems to be brighter than the surrounding holes. This may also happen if an incorrect choice of the CS prior regularization parameter $\lambda_1$ results in excessive blurring.}}

\textbf{Response:} Despite tuning $\lambda_1$, In Fig. 19(e) (previously Fig.10(e) of the old version), the information about the new region (within RoI)  is present only in the measurements of the test, and is absent in all of the templates. This is unlike the case for the surrounding holes, the information about which is present both in the measurements of the test and the templates. Hence, the reconstruction of the hole in the RoI is not as sharp as the other holes.\\

\textcolor{blue}{\textbf{R1-C9:}\textit{Some relatively minor issues are below- Page 3, line 7, section II: Consider defining longitudinal study.}}

\textbf{Response:} We have now defined longitudinal study in the paper (Sec. 1). Longitudinal studies here refers to the acquisition of sequential CT scans of the same subject to track time-evolving changes within the subject's interior.  \\

\textcolor{blue}{\textbf{R1-C10:} \textit{Images in Fig. 3 seem to be clipped in the lower left along a circular arc! Are all reconstructions within a circular outer region of interest?}}

\textbf{Response:} All the reconstructions are within the circular region for this dataset. The ground-truth for this dataset consists of reconstructions from a proprietary software used in the CT machine at the Tata Memorial Hospital, Mumbai. The  RoI was chosen by the proprietary software and hence the exact reason for its choice is known only to the vendors. Based on inputs from physicians at the Centre, we have ensured that the RoI indeed encompasses the regions of interest, i.e. the organ in which ablation is being performed.\\

\textcolor{blue}{\textbf{R1-C11:}\textit{In Fig. 8, what is (g) combined? Also, there is no (h) but is mentioned in caption.}}

\textbf{Response:} The caption has now been correctly renamed to (g). 
By `combined', we denote the weight map computed as per Eq.7.  This equation incorporates the use of the eigen-space of the templates reconstructed from various methods (such as ART, SART, SIRT, etc.), and pilot reconstructions of the test,  again reconstructed from various methods. In Eq.7, the min(.) operator ensures that we select the new regions that are unanimously detected by all the methods of reconstruction. Hence, the word `combined' denotes that all the reconstruction methods are combined to give information about the new regions of the test.\\

\textcolor{blue}{\textbf{R1-C12:}\textit{ Try to mention the actual number of views/projections instead as a percentage. The percentage only makes sense when you are comparing against Nyquist limit for views. For instance, the total number of views for Potato dataset is 900, which is simply too many for a reconstruction size of 150x150. For such a small reconstruction, 900 is not a ``typical'' number views. It may be more ``typical'' to use 150 views in standard practice. So, expressing views as a percentage of 900 is confusing.}}

  \textbf{Response:} Just to clarify, as mentioned in the paper, the 900 views for the potato dataset was used to reconstruct the ground-truth 3D volume of size 150 x 150 x 100, and not a 2D slice of size 150 x 150.  Each of the projection images was of size 150 x 150.

Since our imaging method is circular cone beam projection, let us first assume a 2D example. Consider a circle of radius R=1 that envelops an unknown 2D region X. Then, the circumference of the circle in pixel units will be $2\pi R_p$, where$ R_p$ represents the radius in pixel units, i.e., the number of image-pixels that fit within the radius of the circle. Now, let us assume that we want to pass rays around a half of a circle (due to symmetry). We can reasonably assume that a set of $(2*\pi*R_p)/2$ angles will be ``sufficient'' to faithfully reconstruct X.
\begin{itemize}
\item Given size of the 2D object $= 200 x 200$, the length (in pixel units) of the diagonal of this image $= 200*\sqrt(2)$, and this is twice the radius of the enclosing circle.
\item Since our imaging method is circular cone beam projection, we assume a circle to tightly bound the object.
\item $R_p = 282.84/2 = 141.4$
\item No. of views $= 2*\pi*R_p = 888$ views
\end{itemize}

Similarly, in the case of 3D, assume the object is enclosed within a sphere of unit radius R. Let $R_v$ denote the radius in voxel units, i.e., number of object-voxels that fit within the radius of the sphere. Hence, in 3D, one way to compute sufficient number of views would be the following:
\begin{itemize}
\item Given size of the object scanned $= 150 x 150 x 100$, the length of the space diagonal of this cuboid = $\sqrt{(100^2 + 100^2 + 150^2)}$
\item Since our imaging method is circular cone beam projection, we assume a sphere tightly bounding the object.
\item The radius of this sphere in voxel units ($R_v$) will be $\sqrt{(100^2 + 100^2 + 150^2)}/2 = 103$
and, surface area of the sphere $= 4*\pi*(R_v)^2 = 133320$.
\item If we want to pass at least one ray for every surface voxel of this sphere, we will need 133320/2 (since sphere is symmetrical, and ray at 30 deg will pass through same voxels as ray at 30 +180 deg) = 66658 views. 
\end{itemize}
Hence our choice of 900 views for reconstruction of the ground-truth is not exceedingly large. It just happens to be sufficient due to the homogenous structure of the interior of the object (potato).

Since our gold-standard for measuring accuracy of our technique's reconstruction is the ground-truth reconstruction obtained from 900 views (for the potato dataset), we have measured our achieved reduction in views as a fraction of the views used for reconstructing ground-truth. \\

\textcolor{blue}{\textbf{R1-C13:}\textit{ Hard to notice the features within the ROI in Fig. 15. It may help to present images that zoom into the ROI.}}

\textbf{Response:} The zoomed-in RoI is now shown in Fig. 16. \\

\textcolor{blue}{\textbf{R1-C14:}\textit{ In section V (B), how was the cross-validation or empirical selection of $\lambda_1$ and $\lambda_2$ done? Did you use SSIM as a comparison metric? Did you use any particular object prior image for cross-validation? If so, which image did you use? }}

\textbf{Response:} In our earlier submission, $\lambda_1$ and $\lambda_2$ values were chosen by reconstructing the test volume by sweeping through a range of values and selecting the set of values that gave a reasonable visual quality. In the current version of the paper, we had first chosen $\lambda_1$ as that value which maximizes the SSIM of the l1-ls reconstruction. This value was retained for uniform and spatially-varying prior based reconstruction as well. $\lambda_2$ was chosen clairvoyantly,  i.e., based on the value that gave the best visual results on the test.\\

\textcolor{blue}{\textbf{R1-C15:}\textit{ You are allowed to submit documents or media as supplementary material. Instead of posting them on a dropbox, you could submit them as supplementary material to the journal. You could also use supplementary material to add additional text or figures to reduce number of pages in main paper.}}

\textbf{Response:} Thank you for the suggestion. We have now submitted the supplementary material  on the publication portal. \\

\textcolor{blue}{\textbf{R1-C16:}\textit{ To save space and if you feel comfortable, you could move the section III (A) (1) on patch based techniques to supplementary since it is not a contribution of your paper.}}

\textbf{Response:} In order to save space and for greater clarity, we have now moved the discussion on patch-based techniques to supplementary material.

\section{Response to Reviewer 2}
(We have numbered these comments as \textbf{R2-Cx}, and italicized for clarity)\\

\textcolor{blue}{\textbf{R2-C1.}\textit{ I have one main question concerning Table 1, where I notice FDK gives for the ROI much better SSIM value than the variants of the proposed method. What is the reason of this? Why can then the authors state that their method is better than FDK? A bit more detailed explanation would be satisfactory.}}

\textbf{Response:} We hypothesize that because the volume of this dataset (potato) is very homogenous (without intricate  structures), the test measurements capture sufficient information about the new regions even with $5\%$ views and hence FDK performs very well in the exact region of interest (shown as red RoI in Fig. 19(a)). However, as we expand the region of interest (green and cyan RoI in Fig. 19a), the prior-based methods perform better than FDK (please refer Table 8) in that they minimize the sub-sampling artefacts.  We have now discussed this in Section 8. B - ``Reconstruction of homogenous data''.
Had the new region been embedded within an intricate background (like the sprouts and okra), its reconstruction does give rise to artefacts as seen in Figs.13-b and 15-b.

Beside this, I only have minor comments:\\

\textcolor{blue}{\textbf{R2-C2}\textit{. P1, L49, right panel: "a" should not be typeset in italic.}}

\textbf{Response:} The italicized `a' here is used to emphasize the selection of `any one' particular template amongst the many available ones. So, we retain the typeset on ``a'' and for greater clarity, italicize the word `particular' as well . The statement now reads:
``there is the key issue of choice of a particular previously scanned object among the many previously acquired scans.''\\

\textcolor{blue}{\textbf{R2-C3.}\textit{P2, L31, left panel: The subtitle should be typeset in bold.}}

 \textbf{Response:} Accepted. The typeset has been changed.\\

\textcolor{blue}{\textbf{R2-C4. }\textit{P2, L50, left panel: ``reconstruction-'' should be corrected to ``reconstruction -''}}

 \textbf{Response:} Accepted. This has been corrected.\\

\textcolor{blue}{\textbf{R2-C5.}\textit{P5, L10, left panel: ``Eq 6'' should be corrected to ``Eq. 6'' (same in P6, L54, right panel}}

 \textbf{Response:} Accepted. This has been corrected, and the equation has now been moved to  supplementary material (Eq.2). \\

\textcolor{blue}{\textbf{R2-C6.}\textit{ P6, L17, left panel: ``i.e'' should be replaced with ``i.e.'' (correct each further occurrence}}

 \textbf{Response:} As per the conventional use, ``i.e'' has now been replaced by ``i.e.,'' in all occurrences in the paper.\\

\textcolor{blue}{\textbf{R2-C7. }\textit{P6, L42, left panel: ``Eqn. 8'' should be corrected ``Eq. 8'' (same in P7, L19, left panel}}

  \textbf{Response:} Accepted. These have been corrected.\\

 \textcolor{blue}{\textbf{R2-C8.}\textit{ Caption of Fig. 8: The correct form is (a)-(f) and (g)}}

  \textbf{Response:} Accepted. This has been corrected.\\

 \textcolor{blue}{\textbf{R2-C9.}\textit{ P6, L40, right panel: Subtitle should be typeset in bold}}

  \textbf{Response:} Accepted. The typeset has been changed.\\

 \textcolor{blue}{\textbf{R2-C10.}\textit{ P7, L3, and L7: ``proposed methods'' <--> "proposed method". Choose one.}}

 \textbf{Response:} In Sec.6, we use ``Proposed method'' to refer to uniform prior-based method, and in Sec.8 we use ``Proposed method'' to refer to spatially varying prior-based method.\\

\textcolor{blue}{\textbf{R2-C11.}\textit{ Caption of Figs 10, 12, and 13: ``Unselective prior'' should be typeset in two lines instead of three.}}

  \textbf{Response:} Accepted. This has been typeset.\\

 \textcolor{blue}{\textbf{R2-C12.}\textit{ P7, L50, left panel: Replace ``Figs. 9'' with ``Fig. 9''}}

  \textbf{Response:} Accepted. This has been corrected.\\

 \textcolor{blue}{\textbf{R2-C13.}\textit{ P7, L28, right panel: do not use bold typesetting here}}

  \textbf{Response:} Accepted. This has been corrected.\\

 \textcolor{blue}{\textbf{R2-C14.}\textit{ Caption of Fig. 15: ``Letters missing''}}

  \textbf{Response:} Accepted. This has been corrected.\\

 \textcolor{blue}{\textbf{R2-C15.}\textit{ P8, L49, right panel: Correct ``shows'' to ``show''}}

 \textbf{Response:} Accepted. This has been corrected.\\

 \textcolor{blue}{\textbf{R2-C16.}\textit{ Caption of Fig. 16: ``slice-8'' should be replaced with ``image-8''}}

 \textbf{Response:} Accepted. This has been corrected.\\

 \textcolor{blue}{\textbf{R2-C17.}\textit{ P9, L20, right panel: Move [16] to the second place.   }}

 \textbf{Response:} Accepted. This had been corrected.\\

\textcolor{blue}{\textbf{R2-C18.}\textit{P9, L34, right panel: ``[38](FDK'' space is missing}}

 \textbf{Response:} Accepted. This has been corrected.\\

 \textcolor{blue}{\textbf{R2-C19.}\textit{P9, L36, right panel: ``in-dept'' should be corrected to ``in-depth'', ``in'' should be corrected to ``is''}}

 \textbf{Response:} Accepted. These have been corrected.\\

 \textcolor{blue}{\textbf{R2-C20.}\textit{ Caption of Fig. 17: ``weight maps'' should be corrected to ``weights maps''}}

\textbf{ Response:} Accepted. This has been corrected to `weights-maps' in all occurrences in the paper.\\

 \textcolor{blue}{\textbf{R2-C21.}\textit{ Acknowledgement: ``Dr.Andrew Kingston'' space is missing}}

\textbf{ Response:} Accepted. This has been corrected.

\bibliography{tci_ref}
\end{document}
